FMA: A Dataset For Music Analysis

### 2017-03-17 fma.tex
size comparison between datasets

@@

Content-based music information retrieval tasks are typically solved with a two-stage approach: engineered features are extracted from music audio signals, and are then used as input to a regressor or classifier.
Although that approach was dominant in the past, feature learning and end-to-end learning (from signal to label) have started to receive more attention from the MIR community in recent years. 
The primary goal of this dataset is to enable researchers to train large models, which require lots of training data, which could potentially avert the semantic gap currently observed between the extracted low-level features such as MFCCs and the high-level targets such as genre.

@@

%%%%%%%%%%%%%%%%%%%
\section{Introduction} % and Motivation}
%%%%%%%%%%%%%%%%%%%

@@

\noindent
{\bf Available music datasets and their limitations.} In music analysis, three datasets have been widely used by the international society for music information retrieval (ISMIR)\footnote{\url{http://www.ismir.net/}}: the GTZAN, TagATune, and MSD (Million Song Dataset) datasets. However each dataset come with some limitations:
We discuss below some of the most related datasets, see \tabref{tab:datasets} for a more comprehensive list.
\tabref{tab:datasets} shows the most common datasets used for audio-based / content-based MIR.
\begin{description}
	\item[GTZAN] \cite{gtzan} is a collection of 1000 songs with 10 music genres. Each song is represented by a 22,050Hz Mono 16-bit wav audio file of 30sec. It is the first benchmark MGR dataset to have been made publicly available, and as a result continues to be the most used public dataset for MGR \cite{mgr_eval}. A complete study, and critic, of this dataset was done in \cite{gtzan_critic_1}, and the dataset is available online. The main limitations of GTZAN is the legality of the dataset, the small size, no complete meta-data regarding artist names and song titles, and no additional meta-data like ratings.
	\item[MagnaTagATune] \cite{magnatagatune} is a popular dataset of 5,405 source songs from 230 artists, cut in 25,863 clips. The music was collected from the \href{https://magnatune.com/}{Magnatune} label and was tagged using the \href{http://tagatune.org/}{TagATune} game. The dataset includes meta-data, audio features and raw audio, although the 16 kHz, 32kbps, mono mp3 are of poor audio quality.
	\item[The Million Song Dataset (MSD)] \cite{msd} is a free and legal collection of 1 million music songs. Each song data is composed of high-level and medium-level audio features provided by  Echonest service and meta-data like artist name, song title, track genre, etc. It has its own dedicated website with related code and additional datasets. The very large scale of this music dataset would make it an ideal candidate for deep learning, which works best with large datasets. However, deep learning techniques work directly on the raw data (audio tracks in this case, like raw image pixels in computer vision) and not on pre-processed audio features given by Echonest. This prevents the application of deep learning on this dataset. Finally, Echonest reassigned the indexing of the MDS songs with its database, which henceworth makes (almost) impossible the use of the most music recent features developed by Echonest.
		While researchers have been able to download sample audio from the online service \url{7signal.com} and extract features by themselves, the process is tedious \cite{msd_features}.
	\item[AudioSet] \cite{audioset} is a dataset of 2.1 million annotated 10-second sound clips associated with 527 classes. The ontology is quite broad and covers sounds from music to cars, engines or animals. The raw audio is however not included and has to be downloaded from Youtube. It is not clear of what happens if a referenced video gets deleted.
\end{description}

\begin{table}
	\centering
	\begin{threeparttable}
	\begin{tabular}{lrrcc}
		\toprule
		dataset & \#clips & \#artists & year & audio \\
		\midrule
		\href{https://staff.aist.go.jp/m.goto/RWC-MDB/}{RWC} \cite{RWC} & 465 & - & 2001 & yes \\
		\href{http://calab1.ucsd.edu/~datasets/cal500/}{CAL500} \cite{cal500} & 500 & 500 & 2007 & yes \\
		\href{http://mtg.upf.edu/ismir2004/contest/tempoContest/node5.html}{Ballroom} \cite{ballroom} & 698 & - & 2004 & yes \\
		\href{http://ismir2004.ismir.net/genre_contest/}{ISMIR2004} & 729 & - & 2004 & yes \\
		\href{https://marsyasweb.appspot.com/download/data_sets/}{GZTAN} \cite{gtzan} & 1,000 & $\sim300$ & 2002 & yes \\
		\href{http://www.cp.jku.at/datasets/musiclef/}{MusiClef} \cite{musiclef} & 1,355 & 218 & 2012 & yes \\
		\href{https://labrosa.ee.columbia.edu/projects/artistid/}{Artist20} \cite{artist20} & 1,413 & 20 & 2007 & yes \\
		\href{http://www-ai.cs.uni-dortmund.de/audio.html}{Homburg} \cite{garageband} & 1,886 & - & 2005 & yes \\  % GarageBand
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{Unique} & 3,115 & - & 2010 & no \\
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{1517-Artists} & 3,180 & 1,517 & 2010 & yes \\
		\href{http://www.ppgia.pucpr.br/~silla/lmd/}{LMD} \cite{lmd} & 3,227 & - & 2007 & no \\
		\href{http://anasynth.ircam.fr/home/media/ExtendedBallroom}{EBallroom} \cite{extballroom} & 4,180 & - & 2016 & no\tnote{1} \\
		\href{https://labrosa.ee.columbia.edu/projects/musicsim/uspop2002.html}{USPOP} \cite{uspop} & 8,752 & 400 & 2003 & no \\
		\href{http://calab1.ucsd.edu/~datasets/cal10k/}{CAL10k} \cite{cal10k} & 10,271 & 4,597 & 2010 & no \\ % Swat10k
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{TagATune} \cite{magnatagatune} & 25,863\tnote{2} & 230 & 2009 & yes\tnote{3} \\ % MagnaTagATune
		\href{http://jmir.sourceforge.net/index_Codaich.html}{Codaich} \cite{codaich} & 26,420 & 1,941 & 2006 & no \\ % paper 20,849
		\bf \href{https://github.com/mdeff/fma/}{FMA} & \bf 110,000 & \bf - & \bf 2017 & \bf yes \\
		\href{http://www.omras2.org/}{OMRAS2} \cite{omras} & 152,410 & 6,938 & 2009 & no \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} & 1,000,000 & 44,745 & 2011 & no\tnote{1} \\
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} & 2,100,000 & - & 2017 & no\tnote{1} \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		\item[1] Audio can be downloaded from a web service. % \url{www.ballroomdancers.com} \url{7signal.com} \url{youtube.com}
		\item[2] The 25,863 clips come from 5,405 songs.
		\item[3] Low quality 16 kHz, 32kbps, mono mp3.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Comparison with some other datasets.}
	\label{tab:datasets}
\end{table}

@@

\begin{table}
	\centering
	\begin{threeparttable}
	\begin{tabular}{lrrcc}
		\toprule
		dataset & \#clips & length\tnote{1} & \#days\tnote{2} & size\tnote{3} \\
		\midrule
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{TagATune} \cite{magnatagatune} & 25,863 & 29 & 8.7 & 3 \\ % MagnaTagATune
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} & 2,100,000 & 10 & 243 & - \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} & 1,000,000 & 30, 60\tnote{4} & 541 & 625 \\
		\bf \href{https://github.com/mdeff/fma/}{FMA} & \bf 110,000 & \bf 10-180 & \bf ? & \bf 900 \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		\item[1] Length of available clips in seconds.
		\item[2] Number of days to listen to the whole available audio.
		\item[3] Size of the audio (accounts for duration and quality).
		\item[4] Most excerpts from 7digital are 30 or 60s \cite{msd_features}.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Audio size comparison.}
	\label{tab:size}
\end{table}

@@

Our differentiating factors:
\begin{description}
	\item[Permissive licensing.] MIR research has historically suffered from the lack of publicly available benchmark datasets. Most of these issues stem from the commercial interest in music by record labels, and therefore imposed rigid copyright. All songs are licensed under Creative Commons by the artists and can thus be redistributed.
* In contrast with images or text for which plenty of data is available online
	\item[Audio.] most of the largest datasets are distributed with features, sometimes computed by commercial services like the Echonest. Researchers are wary of those proprietary features and have seek to compute features themselves, e.g. on the MSD \cite{msd_features}. In contrast, FMA provides audio for each song.
	\item[High quality audio.] full-length original audio uploaded by the artist. Stereo mp3 with bitrates varying between x. Audio, if released or available to download, is usually clips of 10 to 30 seconds. To our knowledge, none of the released datasets up to this date come with full-length audio.
	\item[Future proof]: all audio and meta-data can be downloaded as ZIP archives, no need to scrap the web yourself. They are checksummed, have a DOI and are hosted on \href{https://zenodo.org}{zenodo.org}, a long-term digital archive powered by CERN. We thus alleviate the risks of tracks to become unavailable, to change without notice or for online services to shut down.
	% Western / commercial music, how to qualify broadness?
	\item[Reproducible]: we share all the code used to (i) collect the dataset, (ii) analyze it, (iii) extract the sub-sets, (iv) compute the features and (v) the baselines, so that it can be reproduced or extended. As the original data and APIs are public, anybody can recreate the dataset. A train / test split is provided to make research on the FMA reproducible.
	\item[Easy to work with]: working with the dataset only requires to download some archives. Moreover, we provide an helper Python package\footnote\url{https://pypi.python.org/pypi/freemusicarchive} and usage examples as Jupyter notebooks to quick start using the data.
\end{description}

@@

\noindent
{\bf What would be the requirements for an ideal music dataset?}  \\
(1) Availability of raw audio tracks like 30sec or more,\\
(2) Availability of meta-data such as genres, artist, title, year, lyrics, users' ratings, users' comments, etc,\\
(3) Large-scale dataset to be able to sample the high-dimensional distribution of music genres\\
(4) Free and easy access of the dataset,\\
(5) Legality of the dataset, no copyright issue with e.g. open access licence.\\

%%%%%%%%%%%%%%%%%%%
\section{The Dataset} %Introducing the FMA dataset}
%%%%%%%%%%%%%%%%%%%

@@

@@

\section{Proposed tasks} % usage, problems
% List some MIR tasks and propose some who can be done with that dataset

@@

Can be down: genre, artist, popularity prediction, tags, year prediction

@@

\section{Genre Recognition} % MGR, Baselines
% One of the most common task, we give some baselines so that people have a reference about how hard it is.

Music genre recognition (MGR) is one of the most researched areas of MIR.

@@

%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Perspectives}
%%%%%%%%%%%%%%%%%%%

@@

\section{Acknowledgments}

@@

\bibliography{refs}

>>>>

\usepackage{array}

\usepackage{color}
\newcommand{\todo}[1]{{\color{red} #1 }}

@@

Content-based music information retrieval tasks are typically solved with a two-stage approach: engineered features are extracted from music audio signals, and are then used as input to a regressor or classifier.
Although that approach was dominant in the past, feature learning and end-to-end learning (from signal to label) have started to receive more attention from the MIR community in recent years. 
The primary goal of this dataset is to enable researchers to train large models, which require lots of training data, which could potentially avert the semantic gap currently observed between the extracted low-level features such as MFCCs and the high-level targets such as genre.
Hopefully, the release of such amount of easily accessible data will foster research which will ultimately surpass the performance ceiling observed in e.g. genre recognition, as it as been the case in computer vision with the release of ImageNet.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} % and Motivation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\noindent
{\bf Available music datasets and their limitations.} In music analysis, three datasets have been widely used by the international society for music information retrieval (ISMIR)\footnote{\url{http://www.ismir.net/}}: the GTZAN, TagATune, and MSD (Million Song Dataset) datasets. However each dataset come with some limitations:
We discuss below some of the most related datasets, see \tabref{tab:datasets} for a more comprehensive list.
\tabref{tab:datasets} shows the most common datasets used for audio-based / content-based MIR.
\begin{description}
	\item[GTZAN] \cite{gtzan} is a collection of 1000 songs with 10 music genres. Each song is represented by a 22,050Hz Mono 16-bit wav audio file of 30sec. It is the first benchmark MGR dataset to have been made publicly available, and as a result continues to be the most used public dataset for MGR \cite{mgr_eval}. A complete study, and critic, of this dataset was done in \cite{gtzan_critic_1}, and the dataset is available online. The main limitations of GTZAN is the legality of the dataset, the small size, no complete meta-data regarding artist names and song titles, and no additional meta-data like ratings.
	\item[MagnaTagATune] \cite{magnatagatune} is a popular dataset of 5,405 source songs from 230 artists, cut in 25,863 clips. The music was collected from the \href{https://magnatune.com/}{Magnatune} label and was tagged using the \href{http://tagatune.org/}{TagATune} game. The dataset includes meta-data, audio features and raw audio, although the 16 kHz, 32kbps, mono mp3 are of poor audio quality.
	\item[The Million Song Dataset (MSD)] \cite{msd} is a free and legal collection of 1 million music songs. Each song data is composed of high-level and medium-level audio features provided by  Echonest service and meta-data like artist name, song title, track genre, etc. It has its own dedicated website with related code and additional datasets. The very large scale of this music dataset would make it an ideal candidate for deep learning, which works best with large datasets. However, deep learning techniques work directly on the raw data (audio tracks in this case, like raw image pixels in computer vision) and not on pre-processed audio features given by Echonest. This prevents the application of deep learning on this dataset. Finally, Echonest reassigned the indexing of the MDS songs with its database, which henceworth makes (almost) impossible the use of the most music recent features developed by Echonest.
		While researchers have been able to download sample audio from the online service \href{https://www.7digital.com}{7digital.com} and extract features by themselves, the process is tedious \cite{msd_features}.
	\item[AudioSet] \cite{audioset} is a dataset of 2.1 million annotated 10-second sound clips associated with 527 classes. The ontology is quite broad and covers sounds from music to cars, engines or animals. The raw audio is however not included and has to be downloaded from Youtube. It is not clear of what happens if a referenced video gets deleted.
\end{description}

\begin{table}
	\centering
	\begin{threeparttable}
	\begin{tabular}{lrrcc}
		\toprule
		dataset & \#clips & \#artists & year & audio \\
		\midrule
		\href{https://staff.aist.go.jp/m.goto/RWC-MDB/}{RWC} \cite{RWC} & 465 & - & 2001 & yes \\
		\href{http://calab1.ucsd.edu/~datasets/cal500/}{CAL500} \cite{cal500} & 500 & 500 & 2007 & yes \\
		\href{http://mtg.upf.edu/ismir2004/contest/tempoContest/node5.html}{Ballroom} \cite{ballroom} & 698 & - & 2004 & yes \\
		\href{http://ismir2004.ismir.net/genre_contest/}{ISMIR2004} & 729 & - & 2004 & yes \\
		\href{https://marsyasweb.appspot.com/download/data_sets/}{GZTAN} \cite{gtzan} & 1,000 & $\sim300$ & 2002 & yes \\
		\href{http://www.cp.jku.at/datasets/musiclef/}{MusiClef} \cite{musiclef} & 1,355 & 218 & 2012 & yes \\
		\href{https://labrosa.ee.columbia.edu/projects/artistid/}{Artist20} \cite{artist20} & 1,413 & 20 & 2007 & yes \\
		\href{http://www-ai.cs.uni-dortmund.de/audio.html}{Homburg} \cite{garageband} & 1,886 & - & 2005 & yes \\  % GarageBand
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{Unique} & 3,115 & - & 2010 & no \\
		\href{http://www.seyerlehner.info/index.php?p=1_3_Download}{1517-Artists} & 3,180 & 1,517 & 2010 & yes \\
		\href{http://www.ppgia.pucpr.br/~silla/lmd/}{LMD} \cite{lmd} & 3,227 & - & 2007 & no \\
		\href{http://anasynth.ircam.fr/home/media/ExtendedBallroom}{EBallroom} \cite{extballroom} & 4,180 & - & 2016 & no\tnote{1} \\
		\href{https://labrosa.ee.columbia.edu/projects/musicsim/uspop2002.html}{USPOP} \cite{uspop} & 8,752 & 400 & 2003 & no \\
		\href{http://calab1.ucsd.edu/~datasets/cal10k/}{CAL10k} \cite{cal10k} & 10,271 & 4,597 & 2010 & no \\ % Swat10k
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{TagATune} \cite{magnatagatune} & 25,863\tnote{2} & 230 & 2009 & yes\tnote{3} \\ % MagnaTagATune
		\href{http://jmir.sourceforge.net/index_Codaich.html}{Codaich} \cite{codaich} & 26,420 & 1,941 & 2006 & no \\ % paper 20,849
		\bf \href{https://github.com/mdeff/fma/}{FMA} & \bf 110,000 & \bf - & \bf 2017 & \bf yes \\
		\href{http://www.omras2.org/}{OMRAS2} \cite{omras} & 152,410 & 6,938 & 2009 & no \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} & 1,000,000 & 44,745 & 2011 & no\tnote{1} \\
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} & 2,100,000 & - & 2017 & no\tnote{1} \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		\item[1] Audio can be downloaded from a web service. % \url{www.ballroomdancers.com} \url{7digital.com} \url{youtube.com}
		\item[2] The 25,863 clips come from 5,405 songs.
		\item[3] Low quality 16 kHz, 32kbps, mono mp3.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Comparison with some other datasets.}
	\label{tab:datasets}
\end{table}

@@

\begin{table*}[t]
	\centering
	\begin{threeparttable}
		\begin{tabular}{lr
			>{$}r<{$}
			@{}>{${}={}$}c@{}
			>{$}l<{$}
			>{$}c<{$}
			cc}
		\toprule
		dataset & \#samples & \multicolumn{3}{c}{dimensionality} & \text{scale} & size [GB] & size [days] \\
		\midrule
		\href{http://mirg.city.ac.uk/codeapps/the-magnatagatune-dataset}{TagATune} \cite{magnatagatune} &
			25,863 & 29\cdot16\cdot10^3\cdot1 && 4.6\cdot10^5 & 1.2\cdot10^{10} & 3 & 8.7 \\ % MagnaTagATune
		\href{https://research.google.com/audioset/}{AudioSet} \cite{audioset} \tnote{1} &
			2,100,000 & 10\cdot44\cdot10^3\cdot2 && 8.8\cdot10^5 & 1.8\cdot10^{12} & - & 243 \\
		\href{https://labrosa.ee.columbia.edu/millionsong/}{MSD} \cite{msd} \tnote{2} &
			1,000,000 & 49\cdot27\cdot10^3\cdot2 && 2.6\cdot10^6 & 2.6\cdot10^{12} & 625 & 541 \\
		\href{https://github.com/mdeff/fma/}{FMA} \tnote{3} &
			110,000 & 180\cdot44\cdot10^3\cdot2 && 1.6\cdot10^7 & 1.7\cdot10^{12} & 900 & 229 \\
		\midrule
		\href{http://yann.lecun.com/exdb/mnist/}{MNIST} \cite{mnist} &
			70,000 & 28\cdot28\cdot1 && 7.8\cdot10^2 & 5.5\cdot10^{7\phantom0} & 0.011 & - \\
		\href{https://www.cs.toronto.edu/~kriz/cifar.html}{CIFAR-10} \cite{cifar} &
			60,000 & 32\cdot32\cdot3 && 3.0\cdot10^3 & 1.8\cdot10^{8\phantom0} & 0.16 & - \\
		\href{http://www.image-net.org}{ImageNet} \cite{imagenet} \tnote{4} &
			14,000,000 & 482\cdot415\cdot3 && 6.0\cdot10^5 & 8.4\cdot10^{12} & 1000 & - \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
		\item[1] \href{https://support.google.com/youtube/answer/6039860}{YouTube recommended} sample rate for music videos.
		\item[2] Average duration and sample rate. Most excerpts from \href{https://www.7digital.com}{7digital} are 30 or 60s and 22 or 44kHz \cite{msd_features}.
		\item[3] Average duration and sample rate. See \todo{ad} for details.
		\item[4] Average resolution. Although most applications resize or crop to $256\cdot256$.
	\end{tablenotes}
	\end{threeparttable}
	\caption{Size comparison. Dimensionality is (length $\cdot$ sample rate $\cdot$ \#channels) for audio and (xdim $\cdot$ ydim $\cdot$ \#channels) for images. Scale is the number of samples times the dimensionality. Size is for a (zipped) archive of all mp3 or jpeg in GB, which is an indication of the quantity of information, e.g. duration or quality. The last column is the number of days to listen to the whole available audio.}
	\label{tab:size}
\end{table*}

@@

Our differentiating factors:
\begin{description}
	\item[Large scale.] Large datasets are needed to avoid overtraining and to effectively learn models that incorporate the ambiguities and inconsistencies that one finds with genre. While FMA is not the largest in term of number of clips, every other dataset with readily available quality audio are two orders of magnitude smaller. A possibly more important size metric here is the total amount of audio, i.e. the sum of the lengths of all clips, in which FMA is in a much better position (see \tabref{tab:size}). For comparison, ImageNet \cite{imagenet}, the largest benchmark dataset in computer vision features 14 million images. Despite a much larger collection, the amount of data is comparable to that of MSD or FMA because of the smaller dimensionality, as shown in \tabref{tab:size}. For statistical learning algorithms, the scale of FMA and MSD is thus comparable to ImageNet.
	\item[Permissive licensing.] MIR research has historically suffered from the lack of publicly available benchmark datasets. Most of these issues stem from the commercial interest in music by record labels, and therefore imposed rigid copyright. All songs are licensed under Creative Commons by the artists and can thus be redistributed.
* In contrast with images or text for which plenty of data is available online
	\item[Audio.] most of the largest datasets are distributed with features, sometimes computed by commercial services like the Echonest. Researchers are wary of those proprietary features and have seek to compute features themselves, e.g. on the MSD \cite{msd_features}. In contrast, FMA provides audio for each song.
	\item[High quality audio.] full-length original audio uploaded by the artist. Stereo mp3 with bitrates varying between x. Audio, if released or available to download, is usually clips of 10 to 30 seconds. To our knowledge, none of the released datasets up to this date come with full-length audio.
	\item[Future proof]: all audio and meta-data can be downloaded as ZIP archives, no need to scrap the web yourself. They are checksummed, have a DOI and are hosted on \href{https://zenodo.org}{zenodo.org}, a long-term digital archive powered by CERN. We thus alleviate the risks of tracks to become unavailable, to change without notice or for online services to shut down.
	% Western / commercial music, how to qualify broadness?
	\item[Reproducible]: we share all the code used to (i) collect the dataset, (ii) analyze it, (iii) extract the sub-sets, (iv) compute the features and (v) the baselines, so that it can be reproduced or extended. As the original data and APIs are public, anybody can recreate the dataset. A train / test split is provided to make research on the FMA reproducible.
	\item[Easy to work with]: working with the dataset only requires to download some archives. Moreover, we provide an helper Python package\footnote\url{https://pypi.python.org/pypi/freemusicarchive} and usage examples as Jupyter notebooks to quick start using the data.
\end{description}

@@

% Do not present like this because we might want representativeness. Which would necessarily include commercial music.

%{\bf What would be the requirements for an ideal music dataset?} \\
%(1) Availability of raw audio tracks like 30sec or more,\\
%(2) Availability of meta-data such as genres, artist, title, year, lyrics, users' ratings, users' comments, etc,\\
%(3) Large-scale dataset to be able to sample the high-dimensional distribution of music genres\\
%(4) Free and easy access of the dataset,\\
%(5) Legality of the dataset, no copyright issue with e.g. open access licence.\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Dataset} %Introducing the FMA dataset}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Genres}

While it is difficult to construct a hierarchy of genres, we follow that of our source.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed tasks} % usage, problems
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% List some MIR tasks and propose some who can be done with that dataset

@@

Can be down: genre, artist, popularity prediction, tags, year prediction
% Cannot: mood, style, annotations

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Genre Recognition} % MGR, Baselines
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One of the most common task, we give some baselines so that people have a reference about how hard it is.
% ground truth for genre: AllMusic Guide (album, artist), Gracenote CDDB (song)

% genre not defined by audio content only
While the utility of music genre recognition (MGR) has been debated, mostly because of its ambiguity and cultural definition, it is widely used and understood by end-users who find it useful to discuss musical categories \cite{mgr_why}. Moreover, it is one of the most researched areas of MIR.

While there certainly is noise in our labels, we trust the artists to have selected the most appropriate set of genres for their own songs.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Perspectives}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgments}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliography{refs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
